### 2010-03-07 papers/icfp-2010-desc/outline.tex
Desc@ICFP: explain the map

>>>>

\begin{structure}
How to read me:
    '<-'  means "because"
    '->'  means "therefore"
    '/>'  means "but"

The spatial tabbing encodes the scope. Things on the same column are
linked by an implicit "and". Things under an argument justify it.

I know, that's fucked up and you hate it. But that's much better to
read that crap than reading my long frenglish sentences a la James
Proust.
\end{structure}
